### 2014-09-06 abstract.tex
minor

\begin{abstract}
Predictive analysis has recently emerged as a promising technique for 
sound detection of multithreading bugs (i.e., without false alarms). 
The idea is to start from an instrumented execution trace, and transform 
it based on the concrete information it provides, such as concrete values 
and memory accesses, to expose bugs, while preserving feasibility. For
example, it may reoder trace events to simulate different thread schedules, 
as long as value flow dependencies are preserved.

Predictive analysis has been successfully applied to data-race detection, 
although the state-of-the-art techniques are overly restrictive in the 
transformations they allow such that their analysis coverage is 
unnecessarily limited.

>>>>

\begin{abstract}
Predictive analysis has recently emerged as a promising technique for 
sound detection of multithreading bugs (i.e., without false alarms). 
The idea is to start from an instrumented execution trace, and transform 
it based on the concrete information it provides, such as concrete values 
and memory accesses, to expose bugs, while preserving feasibility. For
example, the analysis may reorder trace events to simulate different thread schedules, 
as long as value flow dependencies are preserved.

Predictive analysis has been successfully applied to data-race detection, 
although the state-of-the-art techniques are overly restrictive in the 
transformations they allow, sacrificing coverage in return for a conservative soundness guarantee.
